---
title: "Gene expression by tissue vs load"
author: "Aoyue Bi, Daxing Xu"
date: "`r Sys.Date()`"
output: 
  html_document: # html_notebook, html_document
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    number_sections: true
    theme: simplex # default, united, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
    highlight: haddock # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, and breezedark
    # bibliography: bibliography.json
---


# FigS2

```{r setup, echo = T, message = T, warning = F}
library(tidyverse)
# library(RColorBrewer)
# library(ggpubr)
# library(egg)
## eval 代码要不要运行
## echo 代码要不要输出
## include 图要不要输出
## warning 警告要不要输出
## message 默认Bin等信息要不要输出
```

## 两种不同load计算方法和expression tissue的影响
## ①Gene Expression and tissue ① 全基因组统计法
- caption: Deleterious mutation of genes expressed across tissues.
conclusion: Deleterious mutations are depleted in genes expressed in grain and anther.
```{r}
### Step1: 将29万个基因在35个组织中的表达量过滤，只保留高置信度的最长转录本;将Load的结果也合并到HC数据库中

df_expression <- read_tsv("data/011_geneExpression/expressionByTissue.txt.gz")

```
接上
```{r}
dataFile <- c("data/011_geneExpression/001_geneSummary/001_geneSummary_hexaploid.txt.gz")
df_load <- read_tsv(dataFile) %>% 
  select(Transcripts=Transcript,PercentageSyn_Derived,PercentageNonsyn_Derived,PercentageDel_Derived, NonVsSynRatio_SNP, DelVsSynRatio)


dataFile <- c("data/011_geneExpression/geneHC.txt.gz")
df_geneHC <- read_tsv(dataFile) %>% 
  rename(Transcripts = Longest_transcript) %>% 
  left_join(df_expression,by="Transcripts") %>% 
  left_join(df_load,by="Transcripts") 

# write.table(df_geneHC,file="~/Documents/test.txt",quote=F,col.name=T,row.names=F,sep = "\t")

```
接上
```{r}
### Step2： 转换表格，将组织表达 -> 长表
# df_geneHC$`third leaf sheath`
df_geneHC_long <- df_geneHC %>% 
  pivot_longer(cols = `Internode #2`:`third leaf sheath`, names_to = "Tissue",values_to = "TPM") %>% 
  filter(TPM < 0.5)
```
接上
```{r}
### 计算FreSyn和组织的关系
dfstatistic <- df_geneHC_long %>%
  pivot_longer(cols = PercentageSyn_Derived:DelVsSynRatio,names_to = "LoadType",values_to = "LoadValue") %>% 
  filter(!is.na(LoadValue), is.finite(LoadValue)) %>% 
  group_by(LoadType,Tissue) %>% 
  summarise(ave = mean(LoadValue), sd = sd(LoadValue), N = n(), se = sd/sqrt(N))

# write.table(df,file="~/Documents/barplot.txt",quote=F,col.name=T,row.names=F,sep = "\t")

```

接上- 开始画图
### fre del
```{r}
### 将多个组织的命名方式都添加进去，便于排序画图使用
dataFile <- c("data/011_geneExpression/TissueHashMap.txt")
dfTissueHashMap <- read.delim(dataFile) %>% 
  rename(Tissue = Tissue_inRHeader)

AoCase <- "PercentageDel_Derived"

df <- dfstatistic %>% 
  left_join(.,dfTissueHashMap,by="Tissue") %>% 
  filter(LoadType == AoCase) %>% 
  mutate(High_level_tissue=factor(High_level_tissue,levels = c("roots","leaves/shoots","spike","grain"))) %>% 
  arrange(High_level_tissue,-ave) ## 注意排序！！！

### 画图的时候根据数据框的顺序画出来
### 35 个组织的顺序定义
df$Tissue_inOri <- factor(df$Tissue_inOri,levels = df$Tissue_inOri)

colB <- c("#9a784c","#749b64","#e6b700","#b3b563") ## 4个组织的颜色

p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=ave,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=ave-se, ymax=ave+se), width=.2,
                 position=position_dodge(.9))+
  labs(x="",y= "Frequency of del SNPs in CDS")+
  geom_hline(yintercept = 0.00016, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p
 
ggsave(p,filename = "~/Documents/freDel.pdf",height = 5,width = 7)

```
### fre syn
```{r}
### 将多个组织的命名方式都添加进去，便于排序画图使用
dataFile <- c("data/011_geneExpression/TissueHashMap.txt")
dfTissueHashMap <- read.delim(dataFile) %>% 
  rename(Tissue = Tissue_inRHeader)

AoCase <- "PercentageSyn_Derived"

df <- dfstatistic %>% 
  left_join(.,dfTissueHashMap,by="Tissue") %>% 
  filter(LoadType == AoCase) %>% 
  mutate(High_level_tissue=factor(High_level_tissue,levels = c("roots","leaves/shoots","spike","grain"))) %>% 
  arrange(High_level_tissue,-ave) ## 注意排序！！！

### 画图的时候根据数据框的顺序画出来
### 35 个组织的顺序定义
df$Tissue_inOri <- factor(df$Tissue_inOri,levels = df$Tissue_inOri)
colB <- c("#9a784c","#749b64","#e6b700","#b3b563") ## 4个组织的颜色

p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=ave,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=ave-se, ymax=ave+se), width=.2,
                 position=position_dodge(.9))+
  labs(x="",y= "Frequency of syn SNPs in CDS")+
  # geom_hline(yintercept = 0.00016, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p
 
ggsave(p,filename = "~/Documents/freSyn.pdf",height = 5,width = 7)

```
### fre nonsyn
```{r}
### 将多个组织的命名方式都添加进去，便于排序画图使用
dataFile <- c("data/011_geneExpression/TissueHashMap.txt")
dfTissueHashMap <- read.delim(dataFile) %>% 
  rename(Tissue = Tissue_inRHeader)

AoCase <- "PercentageNonsyn_Derived"

df <- dfstatistic %>% 
  left_join(.,dfTissueHashMap,by="Tissue") %>% 
  filter(LoadType == AoCase) %>% 
  mutate(High_level_tissue=factor(High_level_tissue,levels = c("roots","leaves/shoots","spike","grain"))) %>% 
  arrange(High_level_tissue,-ave) ## 注意排序！！！

### 画图的时候根据数据框的顺序画出来
### 35 个组织的顺序定义
df$Tissue_inOri <- factor(df$Tissue_inOri,levels = df$Tissue_inOri)
colB <- c("#9a784c","#749b64","#e6b700","#b3b563") ## 4个组织的颜色

p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=ave,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=ave-se, ymax=ave+se), width=.2,
                 position=position_dodge(.9))+
  labs(x="",y= "Frequency of nonsyn SNPs in CDS")+
  # geom_hline(yintercept = 0.00016, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p
 
ggsave(p,filename = "~/Documents/freNonsyn.pdf",height = 5,width = 7)

```
### ratio del/syn
```{r}
### 将多个组织的命名方式都添加进去，便于排序画图使用
dataFile <- c("data/011_geneExpression/TissueHashMap.txt")
dfTissueHashMap <- read.delim(dataFile) %>% 
  rename(Tissue = Tissue_inRHeader)

AoCase <- "DelVsSynRatio"

df <- dfstatistic %>% 
  left_join(.,dfTissueHashMap,by="Tissue") %>% 
  filter(LoadType == AoCase) %>% 
  mutate(High_level_tissue=factor(High_level_tissue,levels = c("roots","leaves/shoots","spike","grain"))) %>% 
  arrange(High_level_tissue,-ave) ## 注意排序！！！

### 画图的时候根据数据框的顺序画出来
### 35 个组织的顺序定义
df$Tissue_inOri <- factor(df$Tissue_inOri,levels = df$Tissue_inOri)
colB <- c("#9a784c","#749b64","#e6b700","#b3b563") ## 4个组织的颜色

p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=ave,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=ave-se, ymax=ave+se), width=.2,
                 position=position_dodge(.9))+
  labs(x="",y= "Del/syn SNPs in CDS")+
  geom_hline(yintercept = 0.1348, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p
 
ggsave(p,filename = "~/Documents/RatioHGDelVSSyn.pdf",height = 5,width = 7)

### 查看每个组织有多少个基因含有burden值
p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=N,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  labs(x="",y= "Gene number with strongly burden")+
  geom_hline(yintercept = 0.0318, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p


```

### ratio nonsyn/syn
```{r}
### 将多个组织的命名方式都添加进去，便于排序画图使用
dataFile <- c("data/011_geneExpression/TissueHashMap.txt")
dfTissueHashMap <- read.delim(dataFile) %>% 
  rename(Tissue = Tissue_inRHeader)

AoCase <- "NonVsSynRatio_SNP"

df <- dfstatistic %>% 
  left_join(.,dfTissueHashMap,by="Tissue") %>% 
  filter(LoadType == AoCase) %>% 
  mutate(High_level_tissue=factor(High_level_tissue,levels = c("roots","leaves/shoots","spike","grain"))) %>% 
  arrange(High_level_tissue,-ave) ## 注意排序！！！

### 画图的时候根据数据框的顺序画出来
### 35 个组织的顺序定义
df$Tissue_inOri <- factor(df$Tissue_inOri,levels = df$Tissue_inOri)
colB <- c("#9a784c","#749b64","#e6b700","#b3b563") ## 4个组织的颜色

p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=ave,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=ave-se, ymax=ave+se), width=.2,
                 position=position_dodge(.9))+
  labs(x="",y= "Nonsyn/syn SNPs in CDS")+
  # geom_hline(yintercept = 0.00016, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p
 
ggsave(p,filename = "~/Documents/RatioNonsynVSSyn.pdf",height = 5,width = 7)

```

## 查看不同列变量的分布趋势
```{r}
ggplot(df_geneHC_long,aes(x=PercentageSyn_Derived))+
  geom_histogram()

ggplot(df_geneHC_long,aes(x= PercentageDel_Derived))+
  geom_histogram()

ggplot(df_geneHC_long,aes(x=PercentageNonsyn_Derived))+
  geom_histogram()

ggplot(df_geneHC_long,aes(x=DelVsSynRatio))+
  geom_histogram()

ggplot(df_geneHC_long,aes(x= NonVsSynRatio_SNP))+
  geom_histogram()



```




## ②Gene Expression and tissue ② mutation burden
- caption: Deleterious mutation of genes expressed across tissues.
conclusion: Deleterious mutations are depleted in genes expressed in grain and anther.
```{r}
### Step1: 将29万个基因在35个组织中的表达量过滤，只保留高置信度的最长转录本;将Load的结果也合并到HC数据库中
### 第一个数据框
dataFile <- c("data/011_geneExpression/expressionByTissue.txt.gz")
df_expression <- read.delim(dataFile)
```
接上
```{r}
### 第二个数据框
dataFile <- c("data/fromDaxing/Burden_Expression/004_burdenMean_vs_expression/GeneBurden.sum.txt.gz")
df_load <- read.delim(dataFile) %>%
  rename(Gene = geneName)


dataFile <- c("data/011_geneExpression/geneHC.txt.gz")
df_geneHC <- read.delim(dataFile) %>%
  rename(Transcripts = Longest_transcript) %>%
  left_join(.,df_expression,by="Transcripts")  ###合并第1个数据框

## expression 文件与load文件合并
  df_expression_load <- df_load %>%
    left_join(.,df_geneHC,by="Gene")  ###合并第2个数据框

# write.table(df_geneHC,file="~/Documents/test.txt",quote=F,col.name=T,row.names=F,sep = "\t")

```
接上
```{r}
### Step2： 转换表格，将组织表达 -> 长表
df_expression_load_long <- df_expression_load %>%
  pivot_longer(.,cols = Internode..2:third.leaf.sheath, names_to = "Tissue",values_to = "TPM") %>%
  filter(TPM < 0.5)
```
接上
```{r}
### 计算load和组织的关系
dfstatistic <- df_expression_load_long %>%
  # pivot_longer(.,cols = FreSyn:RatioHGDelVSSyn,names_to = "LoadType",values_to = "LoadValue") %>%
  filter(!is.na(Burden), is.finite(Burden)) %>%
  group_by(SlightlyOrStrongly,Tissue) %>% ### 计算不同分类下，不同组织load的平均值 标准差
  summarise(ave = mean(Burden), sd = sd(Burden), n= n(), se = sd/sqrt(n))

write.table(dfstatistic,file="~/Documents/barplot.txt",quote=F,col.name=T,row.names=F,sep = "\t")

```

接上- 开始画图
### strongly burden by individual
```{r}
### 将多个组织的命名方式都添加进去，便于排序画图使用
dataFile <- c("data/011_geneExpression/TissueHashMap.txt")
dfTissueHashMap <- read.delim(dataFile) %>%
  rename(Tissue = Tissue_inRHeader)

AoCase <- "StronglyBurden"

df <- dfstatistic %>%
  left_join(.,dfTissueHashMap,by="Tissue") %>%
  filter(SlightlyOrStrongly == AoCase) %>%
  mutate(High_level_tissue=factor(High_level_tissue,levels = c("roots","leaves/shoots","spike","grain"))) %>%
  arrange(High_level_tissue,-ave) ## 注意排序！！！

### 画图的时候根据数据框的顺序画出来
### 35 个组织的顺序定义
df$Tissue_inOri <- factor(df$Tissue_inOri,levels = df$Tissue_inOri)

colB <- c("#9a784c","#749b64","#e6b700","#b3b563") ## 4个组织的颜色

p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=ave,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=ave-se, ymax=ave+se), width=.2,
                 position=position_dodge(.9))+
  labs(x="",y= "Strongly burden in CDS")+
  geom_hline(yintercept = 0.0318, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p

ggsave(p,filename = "~/Documents/stronglyBurden_in_Tissue.pdf",height = 5,width = 7)

### 查看每个组织有多少个基因含有burden值
p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=n,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  labs(x="",y= "Gene number with strongly burden")+
  geom_hline(yintercept = 0.0318, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p

```

### slightly burden by individual
```{r}
### 将多个组织的命名方式都添加进去，便于排序画图使用
dataFile <- c("data/011_geneExpression/TissueHashMap.txt")
dfTissueHashMap <- read.delim(dataFile) %>%
  rename(Tissue = Tissue_inRHeader)

AoCase <- "SlightlyBurden"

df <- dfstatistic %>%
  left_join(.,dfTissueHashMap,by="Tissue") %>%
  filter(SlightlyOrStrongly == AoCase) %>%
  mutate(High_level_tissue=factor(High_level_tissue,levels = c("roots","leaves/shoots","spike","grain"))) %>%
  arrange(High_level_tissue,-ave) ## 注意排序！！！

### 画图的时候根据数据框的顺序画出来
### 35 个组织的顺序定义
df$Tissue_inOri <- factor(df$Tissue_inOri,levels = df$Tissue_inOri)

colB <- c("#9a784c","#749b64","#e6b700","#b3b563") ## 4个组织的颜色

p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=ave,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=ave-se, ymax=ave+se), width=.2,
                 position=position_dodge(.9))+
  labs(x="",y= "Slightly burden in CDS")+
  geom_hline(yintercept = 0.6534, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p

ggsave(p,filename = "~/Documents/slightlyBurden_in_Tissue.pdf",height = 5,width = 7)

### 查看每个组织有多少个基因含有burden值
p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=n,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  labs(x="",y= "Gene number with strongly burden")+
  geom_hline(yintercept = 0.0318, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p


```






## ③Gene Expression and tissue ②③mutation burden
- caption: Deleterious mutation of genes expressed across tissues.
conclusion: Deleterious mutations are depleted in genes expressed in grain and anther.
```{r}
### Step1: 将29万个基因在35个组织中的表达量过滤，只保留高置信度的最长转录本;将Load的结果也合并到HC数据库中
### 第一个数据框
dataFile <- c("data/011_geneExpression/expressionByTissue.txt.gz")
df_expression <- read.delim(dataFile)
```
接上
```{r}
### 第二个数据框
dataFile <- c("data/fromDaxing/Burden_Expression/004_burdenMean_vs_expression/GeneBurden.averageIndividualBurden.txt.gz")
df_load <- read.delim(dataFile) %>%
  rename(Gene = geneName)


dataFile <- c("data/011_geneExpression/geneHC.txt.gz")
df_geneHC <- read.delim(dataFile) %>%
  rename(Transcripts = Longest_transcript) %>%
  left_join(.,df_expression,by="Transcripts")  ###合并第1个数据框

## expression 文件与load文件合并
  df_expression_load <- df_load %>%
    left_join(.,df_geneHC,by="Gene")  ###合并第2个数据框

# write.table(df_geneHC,file="~/Documents/test.txt",quote=F,col.name=T,row.names=F,sep = "\t")

```
接上
```{r}
### Step2： 转换表格，将组织表达 -> 长表
df_expression_load_long <- df_expression_load %>%
  pivot_longer(.,cols = Internode..2:third.leaf.sheath, names_to = "Tissue",values_to = "TPM") %>%
  filter(TPM < 0.5) %>%
  rename(BurdenbyIndiSum=mean_burden)
  # pivot_longer(.,cols = c(StronglyBurden,SlightlyBurden),names_to = "SlightlyOrStrongly",values_to = "BurdenbyIndiSum")
```
接上
```{r}
### 计算load和组织的关系
dfstatistic <- df_expression_load_long %>%
  # pivot_longer(.,cols = FreSyn:RatioHGDelVSSyn,names_to = "LoadType",values_to = "LoadValue") %>%
  filter(!is.na(BurdenbyIndiSum), is.finite(BurdenbyIndiSum)) %>%
  group_by(SlightlyOrStrongly,Tissue) %>% ### 计算不同分类下，不同组织load的平均值 标准差
  summarise(ave = mean(BurdenbyIndiSum), sd = sd(BurdenbyIndiSum), n= n(), se = sd/sqrt(n))

write.table(dfstatistic,file="~/Documents/barplot.txt",quote=F,col.name=T,row.names=F,sep = "\t")

```

接上- 开始画图
### strongly burden by individual
```{r}
### 将多个组织的命名方式都添加进去，便于排序画图使用
dataFile <- c("data/011_geneExpression/TissueHashMap.txt")
dfTissueHashMap <- read.delim(dataFile) %>%
  rename(Tissue = Tissue_inRHeader)

AoCase <- "StronglyBurden"

df <- dfstatistic %>%
  left_join(.,dfTissueHashMap,by="Tissue") %>%
  filter(SlightlyOrStrongly == AoCase) %>%
  mutate(High_level_tissue=factor(High_level_tissue,levels = c("roots","leaves/shoots","spike","grain"))) %>%
  arrange(High_level_tissue,-ave) ## 注意排序！！！

### 画图的时候根据数据框的顺序画出来
### 35 个组织的顺序定义
df$Tissue_inOri <- factor(df$Tissue_inOri,levels = df$Tissue_inOri)

colB <- c("#9a784c","#749b64","#e6b700","#b3b563") ## 4个组织的颜色

p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=ave,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=ave-se, ymax=ave+se), width=.2,
                 position=position_dodge(.9))+
  labs(x="",y= "Strongly burden in CDS")+
  # geom_hline(yintercept = 1.3076, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p

ggsave(p,filename = "~/Documents/stronglyBurden_in_Tissue.pdf",height = 5,width = 7)

### 查看每个组织有多少个基因含有burden值
p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=n,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  labs(x="",y= "Gene number with strongly burden")+
  geom_hline(yintercept = 1.3076, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p

```

### slightly burden by individual
```{r}
### 将多个组织的命名方式都添加进去，便于排序画图使用
dataFile <- c("data/011_geneExpression/TissueHashMap.txt")
dfTissueHashMap <- read.delim(dataFile) %>%
  rename(Tissue = Tissue_inRHeader)

AoCase <- "SlightlyBurden"

df <- dfstatistic %>%
  left_join(.,dfTissueHashMap,by="Tissue") %>%
  filter(SlightlyOrStrongly == AoCase) %>%
  mutate(High_level_tissue=factor(High_level_tissue,levels = c("roots","leaves/shoots","spike","grain"))) %>%
  arrange(High_level_tissue,-ave) ## 注意排序！！！

### 画图的时候根据数据框的顺序画出来
### 35 个组织的顺序定义
df$Tissue_inOri <- factor(df$Tissue_inOri,levels = df$Tissue_inOri)

colB <- c("#9a784c","#749b64","#e6b700","#b3b563") ## 4个组织的颜色

p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=ave,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=ave-se, ymax=ave+se), width=.2,
                 position=position_dodge(.9))+
  labs(x="",y= "Slightly burden in CDS")+
  geom_hline(yintercept = 0.6534, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p

ggsave(p,filename = "~/Documents/slightlyBurden_in_Tissue.pdf",height = 5,width = 7)

### 查看每个组织有多少个基因含有burden值
p <- df %>%
  ggplot(aes(x= Tissue_inOri, y=n,fill = High_level_tissue)) +
   geom_bar(stat="identity", position=position_dodge()) +
  labs(x="",y= "Gene number with strongly burden")+
  geom_hline(yintercept = 0.0318, color = "gray",linetype="dashed")+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))+
  scale_fill_manual(values = colB)+
  theme(plot.margin=unit(rep(1,4),'lines'))+
  theme(
    panel.background = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=0.7)
    ,legend.position = 'none'
    ,text = element_text(size = 12))

p


```






 



